Resurgence of the Airy function

### 2022-08-16 airy-resurgence.tex
Work on integral equation existence argument
After talking with Angeliki, Piet, Kihyun, and Kihyun's guest.

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{eqnarray}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines

@@

\begin{align*}
\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left|\int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \int_{a \in \partial D} \left(\int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
\end{align*}
Since $\zeta = 0$ and $a$ are both in $\partial D$, and we're assuming that $f$ extends continuously to $\partial D$, we can compute $[\mathcal{G}f](a)$ using an integration path that runs along $\partial D$.
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \int_{a \in \partial D} \left(\int_{a' \in \partial D} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = \int_{a \in \partial D} \left(2\pi R \int_{a' \in \partial D} |g(a, a')\,f(a')|\,\frac{|d\zeta(a')|}{2\pi R} \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\,f\|_1^p\;\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Then, by H\"{o}lder's inequality,
\begin{align*}
\|\mathcal{G}f\|_p^p & \le (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\|f\|_p^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \left( \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R} \right)^{p/q}\,\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Since we're assuming $p \le q$, we can apply Jensen's inequality to the concave function $(\cdot)^{p/q}$ and conclude that
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \|f\|_p^p\;(2\pi R)^p \left( \int_{a \in \partial D} \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R}\,\frac{|d\zeta(a)|}{2\pi R} \right)^{p/q} \\
& = \|f\|_p^p\;(2\pi R)^p\,\|g\|_q^p,
\end{align*}
which simplifies to
\[ \|\mathcal{G}f\|_p \le \|f\|_p\;2\pi R\,\|g\|_q. \]
That means
\[ \|\mathcal{G}\| \le 2\pi R\,\|g\|_q, \]
where the norm of $g$ is taken with respect to the rotation-invariant probability measure on $(\partial D)^2$.

\color{DodgerBlue}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.

We'll study integral operators $\mathcal{G} \acts \holoL{\infty}(\Omega)$ of the form
\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path. The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$. Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}. That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$. The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
\end{align*}
so
\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
In particular, when $\Omega$ is small enough that $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, -1]$.
\subsubsection{Fractional integral equations near a regular singular point}
Consider an integral operator $\mathcal{J}$ of the form
\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
where:
\begin{itemize}
\item $\Lambda$ is a countable subset of $(-\infty, -1)$.
\item $p$, $q$, and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
\item $p$ has a first-order zero at $\zeta = 0$.
\end{itemize}

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{eqnarray}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines
\usepackage{tikz-cd} %% for term norm scratch work

@@

\color{DarkBlue}
\begin{align*}
\|\mathcal{G}f\|_1 & = \int_{a \in \partial D} \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right|\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \left( \sup_D |f| \right) \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
By the maximum principle, $\sup_D |f| = \sup_{\partial D} |f|$, so
\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}. \]
Taking the infimum over all the integration paths we could use to evaluate $[\mathcal{G}f](a)$, we see that
\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \ell_{g, D}(a)\,\frac{|d\zeta(a)|}{2\pi R}. \]
\color{black}

\begin{align*}
\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left| \int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \int_{a \in \partial D} \left( \int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
\end{align*}
Since $\zeta = 0$ and $a$ are both in $\partial D$, and we're assuming that $f$ extends continuously to $\partial D$, we can compute $[\mathcal{G}f](a)$ using an integration path that runs along $\partial D$.
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \int_{a \in \partial D} \left(\int_{a' \in \partial D} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = \int_{a \in \partial D} \left(2\pi R \int_{a' \in \partial D} |g(a, a')\,f(a')|\,\frac{|d\zeta(a')|}{2\pi R} \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\,f\|_1^p\;\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Then, by H\"{o}lder's inequality,
\begin{align*}
\|\mathcal{G}f\|_p^p & \le (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\|f\|_p^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \left( \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R} \right)^{p/q}\,\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Since we're assuming $p \le q$, we can apply Jensen's inequality to the concave function $(\cdot)^{p/q}$ and conclude that
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \|f\|_p^p\;(2\pi R)^p \left( \int_{a \in \partial D} \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R}\,\frac{|d\zeta(a)|}{2\pi R} \right)^{p/q} \\
& = \|f\|_p^p\;(2\pi R)^p\,\|g\|_q^p,
\end{align*}
which simplifies to
\[ \|\mathcal{G}f\|_p \le \|f\|_p\;2\pi R\,\|g\|_q. \]
That means
\[ \|\mathcal{G}\| \le 2\pi R\,\|g\|_q, \]
where the norm of $g$ is taken with respect to the rotation-invariant probability measure on $(\partial D)^2$.

\color{DarkBlue}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
\begin{align*}
\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
\phi & \mapsto \zeta^{-\sigma} \phi
\end{align*}
is an isometry. More generally,
\begin{align*}
\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
f & \mapsto \zeta^{-\delta} f
\end{align*}
is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$. This reduces to the previous statement when $\rho = 0$. For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$. Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.

Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega) := \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade. For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.

We'll study integral operators $\mathcal{G} \maps \holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \sigma}(\Omega)$ of the form
\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path. The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$. Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}. That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell^{\sigma, \rho}_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |\zeta^\sigma f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
& \le \|f\|_{\infty, \sigma} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell^{\sigma, \rho}_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$. The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^{\rho+\lambda}\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell^{\sigma, \rho}_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\lambda}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{-\rho}\,dr \\
& = |\zeta(a)|^{\rho+\lambda} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{-\rho}\,|\zeta(a)|\,dt \\
& = |\zeta(a)|^{\rho+\lambda-\lambda-1-\rho+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
& = \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
& = B(-\lambda,\,1-\rho).
\end{align*}
The beta function $B$ can be written more explicitly as
\[ B(-\lambda,\,1-\rho) = \frac{\Gamma(-\lambda)\,\Gamma(1-\rho)}{\Gamma(1-\lambda-\rho)}. \]
Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
%%In particular, when $\Omega$ is small enough that \textcolor{magenta}{[???]}, the operator on the left-hand side is a contraction of $\holoL{\infty, \sigma}(\Omega)$ for all $\lambda \in (-\infty, -\rho]$.
\subsubsection{Fractional integral equations near a regular singular point}
\textcolor{SeaGreen}{\textbf{Angeliki:} Maybe Kato--Rellich perturbation theory can give existence immediately. It might not give uniqueness, though.}

Consider an integral operator $\mathcal{J}$ of the form
\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
where:
\begin{itemize}
%%\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and $1/p$ is in $\holoL{\infty, 1}(\Omega)$.
%%\item $q$ and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
%%\item $p \in \holoL{\infty, -1}(\Omega)$ and $1/p \in \holoL{\infty, 1}(\Omega)$.
\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and its derivative at $\zeta = 0$ is non-zero.
%%\item $q, r_\lambda \in \holoL{\infty}(\Omega)$.
\item $q$ is a function in $\holoL{\infty}(\Omega)$ that extends holomorphically over $\zeta = 0$.
\item $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$.
%%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
\item $\Lambda$ is a countable subset of $(-\infty, -1)$.
\end{itemize}
Our demand that $p$ and $q$ have convergent power series at $\zeta = 0$ can probably be relaxed; having convergent Novikov series, for example, should be enough. We could also probably replace $\partial^{-1}_{\zeta \text{ from } 0}$ with $\partial^{-1+\delta}_{\zeta \text{ from } 0} \circ \zeta^\delta$ for some $\delta \in [0, 1)$, or adjust the $\partial^\lambda_{\zeta \text{ from } 0}$ similarly.

\textcolor{Indigo}{We want to solve the equation $\mathcal{J}f = 0$. Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, \tau}(\Omega)$.}

Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$. We're assuming that $p$ and $q$ extend holomorphically over $\zeta = 0$, and the additional assumption that $p \in \holoL{\infty, -1}(\Omega)$ implies that $p$ has a first-order zero at $\zeta = 0$.

Since $p$ and $q$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
\begin{alignat*}{2}
p & = p'_0 \zeta &\;+\;& \tilde{p} \\
q & = q_0 &\;+\;& \tilde{q}
\end{alignat*}
with $\tilde{p} \in \holoL{\infty, -2}(\Omega)$ and $\tilde{q} \in \holoL{\infty, -1}(\Omega)$. Then we have
\[ \mathcal{J} = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \]
with
\[ \tilde{\mathcal{J}} = \tilde{p} + \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \]
For any $\tau \in (0, \infty)$,
\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
\[ \mathcal{J} \zeta^{\tau-1} = \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
Then the equation $\mathcal{J}f = 0$ becomes
\begin{align*}
0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \\
0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \\
-p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \\
\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f} \\
\end{align*}

\color{Indigo}
\begin{center}
\begin{tikzcd}[column sep=25mm, row sep=2mm]
& & \holoL{\infty, \rho-1}(\Omega) \\
\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
& & \holoL{\infty, \rho}(\Omega) \\
& & & \holoL{\infty, \rho-1}(\Omega) \\
\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{q}", "\|\tilde{q}\|_{\infty, -1}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 2-\rho) = \frac{1}{2-\rho}}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
& & & \holoL{\infty, \rho}(\Omega) \\
& & & \holoL{\infty, \rho-1}(\Omega) \\
\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-\lambda}"'] \\
& & & \holoL{\infty, \rho}(\Omega)
\end{tikzcd}
\end{center}
\color{DarkBlue}

From \textbf{[our previous discussion]}, we can work out that
\begin{align*}
\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau}(\Omega)\;\text{with} \\
\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}
\end{align*}
and
\begin{align*}
\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, -\tau}(\Omega) \to \mathcal{H}L^{\infty, -1-\tau}(\Omega)\;\text{with} \\
\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{2+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, 1+\tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
\end{align*}
Since $\|\zeta^{-1}\|_{\infty, 1} = 1$, it follows that
\begin{align*}
\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, -\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau}(\Omega)\;\text{with} \\
\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{2+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, 1+\tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
\end{align*}
